Identity Blockchain - Proof of Identity

### 2022-07-24 paper.tex
PoI paper general editing

\lstset{
	language=circom,
	backgroundcolor=\color{lightgray},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b
}

\newcommand{\khk}{K_{P}}
\newcommand{\khkp}{$K^{-1}[\text{HK}]$}
\newcommand{\kid}{K_{ID}}
%\newcommand{\kid}{$K$}
\newcommand{\todo}[1]{\fbox{\parbox{\linewidth}{\textcolor{red}{#1}}}}
\newcommand{\iv}{$IV(\text{\identity})$}
\newcommand{\sigid}{$K^{-1}[CA](K[Identity])$}
\newtheorem{problem}{Problem}
\newenvironment{solution}
  {\emph{Solution:}}
  {\hfill $\square$}
\newcommand{\pbc}{\textit{Identity Blockchain}}

@@

\section{Notation}
\vspace{10px}
 \arrayrulecolor{gray}
\begin{tabular}{p{0.16\linewidth}| p{0.81\linewidth}}
  $(K, K^{-1})$ & \ \ Pair of public key $K$ and the corresponding private key $K^{-1}$ \\[3px]
	$K(value)$ & \ \ String $value$ encrypted with a public key $K$ \\[3px]
	$K^{-1}(value)$ & \ \ String $value$ encrypted with a private key $K^{-1}$ \\[3px]
  $H$ & \ \ zk-SNARK-friendly hash function \\[5px]
 \hline \\
   $Nin$ & \ \ Unique state-issued personal \textit{National Identification Number}\\[3px]
   $CA$ & \ \ Certificate Authority \\[3px]
   $eID$ & \ \ Electronic identification document \\[3px]
	$\kid$ & \ \ CA-certified public key of eID\\[3px]
  $\khk$ & \ \ Person key, unique public key used to access \pbc{}

@@

\newpage
\section{Registering $\kid$}
Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsKid).$$
\begin{enumerate}[leftmargin=0cm]
\item[] \underline{Pseudo-solidity code}

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint => uint) public ninKidUsed;
  mapping(uint => bool) public kidInvalid;

  function registerKid(
    uint hNin, // hNin = H(Nin)
    uint vKid, // vKid = KidPrivate("registerKid")
		uint[2] memory proofPointA,
		uint[2][2] memory proofPointB,
		uint[2] memory proofPointC,
		bool invalidate
  ) public {
		//Setting public arguments
		uint[] memory inputValues = new uint[](2)
		inputValues[0] = hNin;
		inputValues[1] = vKid;

		require(
			verifyProof(
				proofPointA,
				proofPointB,
				proofPointC,
				inputValues
			)
		);

@@

 		uint previousVKid = ninKidUsed[hNin];
    if (previousVKid != vKid and invalidate == true) {
			//If they are different, we need to invalidate old Kid
			kidInvalid[previousVKid] = true;
		}
		require(!kidInvalid[vKid]);

@@

@@

Using https://github.com/zkp-application/circom-rsa-verify for now, MIT license.
Which probably doesn't work, we should check (sha256?). \\
The next line is used on a file of shape:\\
-----BEGIN PUBLIC KEY-----\\
...\\
-----END PUBLIC KEY-----\\
-----BEGIN CERTIFICATE-----\\
...\\
-----END CERTIFICATE-----\\
We assume: \\
	modulus = Subject Modulus\\
	exp = Subject Exponent\\
openssl x509 -in Identification.pem -text -noout\\

Statements we need to check:
\begin{itemize}
	\item CA is an accepted CA by \pbc{}
		\begin{itemize}
			\item A set representation  exists on blockchain which contains CA public keys (CA-public-keys).
			\item Verify inclusion of the CA in cert in CA-public-keys.
			\item A set representation exists on blockchain which has all the revoked CA public keys (Revoked-CA-public-keys).
			\item Verify exclusion of the CA in cert from Revoked-CA-public-keys.
			\item Verify CA validity with respect to time (maybe blockchain)
		\end{itemize}
	\item Cert CA signed 
		\begin{itemize}
			\item the Kid
			\item x509 Subject that contains Nin in the right place in the subject
			\item verify Validity of x509 cert with respect to time
		\end{itemize}
	\item Kid is not on revoked certs list by CA (blockchain hosted list)
	\item Kid decrypts vKid into clear text "registerKid".
\end{itemize}

@@

	//private:
	signal input Nin;
	//Kid, CA signature
	singal input exp[rsaNumberOfWords];
	signal input sign[rsaNumberOfWords];
	signal input modulus[rsaNumberOfWords];

@@

\item[] \underline{Features}
    \begin{itemize}
      \item[] \textbf{Sybil resistance} \\ A Person is prevented from registering more than one $\khk$, e.g. by using different identification documents issued for the same $Nin$.
          \vspace{5px}
      \item[] \textbf{Fix for the loss of eID} \\ A Person who has lost a previously registered $\kid$, e.g. due to loss of eID, can overwrite it by registering a new $\kid$.
          \vspace{5px}
      \item[] \textbf{Identity theft damage control} \\ If a Person overwrites the previous $\kid$ with a new one, the identity Thief loses access to services that verify the entire identity chain.
    \end{itemize}

\item[] \underline{Remarks}
\begin{itemize}
\item[i)] An entity that knows $\kid$, e.g. the CA who certified the corresponding eID, can know that the Person has registered $\kid$ on \pbc{}.
\item[ii)] Reasoning for the choice of arguments: if $H(Nin, \kid^{-1}("register\kid"))$ was used as an argument, then if someone tried to register with two different ids, we couldn't tell if $Nin$ was already used. On the other hand, the choice of arguments $Nin$ and $\kid^{-1}("register\kid")$ would be almost the same as $hNin$ and $\kid^{-1}("register\kid")$, because you can brute force all the possible $Nin$s and find the corresponding $hNins$.
\end{itemize}
\end{enumerate}

\newpage
\section{Registering $\khk$}
Register $\khk$ on \pbc{} by calling $$register\khk(Nin\kid, Nin\kid\khk, proof),$$
  where:
    \begin{enumerate}
      \item[] $Nin\kid=H(Nin,\kid^{-1}("register\khk"))$
      \item[] $Nin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$.
    \end{enumerate}
\begin{enumerate}[leftmargin=0cm]
\item[] \underline{Pseudo-solidity code}

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint => uint) public ninKidKpUsed;

  function registerKp(
    uint hNinKid,
    uint hNinKidKp,
		uint[2] memory proofPointA,
		uint[2][2] memory proofPointsB,
		uint[2] memory proofPointC
  ) public {

		//Setting public arguments
		uint[] memory inputValues = new uint[](2)
		inputValues[0] = hNinKid;
		inputValues[1] = hNinKidKp;

		require(
			verifyProof(
				proofPointA,
				proofPointsB,
				proofPointC,
				inputValues
			)
		);

    ninKidKpUsed[hNinKid] = hNinKidKp;
  }
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}
\item[] \underline{Features}
\begin{itemize}
      \item[] \textbf{Sybil resistance} \\ $\khk$ is a unique public key bound to the Person on the \pbc{}. By design, the Person cannot have two valid $\khk$ keys at the same time.

@@

\item[] \underline{Remarks}
\begin{itemize}
\item[i)] Reasoning behind the choice of arguments:
We want to connect $Nin$ with $\khk$ in a unique, but untraceable way.
If we only used $Nin\kid\khk$ then if someone used multiple $\khk$s we wouldn't be able to prove the connection to $Nin$ (i.e. they could register a lot of $\khk$s).
Hashing connects arguments, and makes them opaque without the knowledge of arguments (which in this case include private keys), so the arguments are opaque without the knowledge of private keys.
\end{itemize}

@@

\newpage
\underline{Pseudo-circom code}
Statements we need to check:
\begin{itemize}
	\item CA
\end{itemize}

>>>>

\lstset{
	language=circom,
	backgroundcolor=\color{verylightgray},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b
}

\newcommand{\khk}{K_{H}}
\newcommand{\khkp}{$K^{-1}[\text{HK}]$}
\newcommand{\kid}{K_{ID}}
%\newcommand{\kid}{$K$}
\newcommand{\todo}[1]{\fbox{\parbox{\linewidth}{\textcolor{red}{#1}}}}
\newcommand{\iv}{$IV(\text{\identity})$}
\newcommand{\sigid}{$K^{-1}[CA](K[Identity])$}
\newtheorem{problem}{Problem}
\newenvironment{solution}
  {\emph{Solution:}}
  {\hfill $\square$}
\newcommand{\pbc}{\textit{Identity Blockchain}}

@@

\section{Notation}
\vspace{10px}
 \arrayrulecolor{gray}
\begin{tabular}{p{0.16\linewidth}| p{0.81\linewidth}}
  $(K, K^{-1})$ & \ \ Pair of public key $K$ and the corresponding private key $K^{-1}$ \\[3px]
	$K(value)$ & \ \ String $value$ encrypted with a public key $K$ \\[3px]
	$K^{-1}(value)$ & \ \ String $value$ encrypted with a private key $K^{-1}$ \\[3px]
  $H$ & \ \ zk-SNARK-friendly hash function \\[5px]
 \hline \\
   $Nin$ & \ \ Unique state-issued personal \textit{National Identification Number}\\[3px]
   $CA$ & \ \ Certificate Authority \\[3px]
   $eID$ & \ \ Electronic identification document \\[3px]
	$\kid$ & \ \ CA-certified public key of eID\\[3px]
  $\khk$ & \ \ Human key, unique public key to access \pbc{}

@@

\newpage
\section{Registering $\kid$}
Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), invalidate\kid, verifyProofArguments).$$
\begin{enumerate}[leftmargin=0cm]

	\item[] \underline{Pseudo-solidity code}

	\hfill\begin{minipage}{\dimexpr\textwidth-20px}
	\begin{lstlisting}[language=Solidity]
	pragma solidity ^0.8.0;

	mapping(uint => uint) public ninKidUsed;
	mapping(uint => bool) public kidInvalid;

	function registerKid(
		uint hNin, // hNin = H(Nin)
		uint vKid, // vKid = KidPrivate("registerKid")
		bool invalidateKid,
		uint[2] memory proofPointA,
		uint[2][2] memory proofPointB,
		uint[2] memory proofPointC
	) public {
		// Setting public arguments
		uint[] memory inputValues = new uint[](2);
		inputValues[0] = hNin;
		inputValues[1] = vKid;

		require(
			verifyProof(proofPointA, proofPointB, proofPointC, inputValues)
		);

@@

		uint previousVKid = ninKidUsed[hNin];
		if (previousVKid != vKid && invalidateKid == true) {
			// If they are different, invalidate old Kid
			kidInvalid[previousVKid] = true;
		}
		require(!kidInvalid[vKid]);

@@

	\item[] Features
    \begin{itemize}
      \item[] \textbf{Sybil resistance} \\ A Person is prevented from registering more than one $\khk$, e.g. by using different eIDs issued for the same $Nin$.
          \vspace{5px}
      \item[] \textbf{Fix for the loss of eID} \\ A Person who has lost a previously registered $\kid$, e.g. due to loss of eID, can overwrite it by registering a new $\kid$.
          \vspace{5px}
      \item[] \textbf{Identity theft damage control} \\ If a Person overwrites the previous $\kid$ with a new one, the identity Thief loses access to services that verify the entire identity chain.
    \end{itemize}

\item[] Remarks
\begin{itemize}
\item[i)] An entity that knows $\kid$, e.g. the CA who certified the corresponding eID, can know that the Person has registered $\kid$ on \pbc{}.
\item[ii)] Reasoning for the choice of arguments $H(Nin)$ and $\kid^{-1}("register\kid")$: 
\begin{itemize}
	\item[-] if $H(Nin, \kid^{-1}("register\kid"))$ was instead used, then if someone tried to register with two different eIDs, we couldn't tell if $Nin$ was already used. 
	\item[-] the choice of arguments $Nin$ and $\kid^{-1}("register\kid")$ would be almost the same as $H(Nin)$ and $\kid^{-1}("register\kid")$, because you can brute force all the possible $Nin$s and find the corresponding $H(Nin)$s.
\end{itemize}
\end{itemize}

@@

Statements we need to check:
\begin{itemize}
	\item[1)] CA is accepted by \pbc{} (assumption: the set representations of \textit{CA-public-keys} and \textit{revoked-CA-public-keys} lists exist on \pbc{}):
		\begin{itemize}
			\item[i)] inclusion of the CA in cert in \textit{CA-public-keys}.
			\item[ii)] exclusion of the CA in cert from \textit{revoked-CA-public-keys}.
		\end{itemize}
		Verify CA validity with respect to time (maybe on \pbc{})!
	\item[2)] Cert CA signed: 
		\begin{itemize}
			\item[i)] $\kid$
			\item[ii)] x509 Subject that contains $Nin$ in the right place in the subject
		\end{itemize}
		Verify validity of x509 certificate with respect to time!
		\item[3)] $\kid$ is not revoked by CA (\pbc{} hosted list)
	\item[4)] $\kid$ decrypts $\kid^{-1}("register\kid")$ into clear text "registerKid".
\end{itemize}

For now, we're using the MIT-licensed \href{https://github.com/zkp-application/circom-rsa-verify}{Circom RSA signature verify}, which probably doesn't work - we should check (sha256?). \\

The next line is used on a file of shape:\\
-----BEGIN PUBLIC KEY-----\\
...\\
-----END PUBLIC KEY-----\\
-----BEGIN CERTIFICATE-----\\
...\\
-----END CERTIFICATE-----\\

We assume: \\
	modulus = Subject Modulus\\
	exp = Subject Exponent\\
openssl x509 -in Identification.pem -text -noout\\

@@

	//private:
	signal input Nin;
	//Kid, CA signature
	signal input exp[rsaNumberOfWords];
	signal input sign[rsaNumberOfWords];
	signal input modulus[rsaNumberOfWords];

@@

\newpage
\section{Registering $\khk$}
Register $\khk$ on \pbc{} by calling $$register\khk(HNin\kid, HNin\kid\khk, \khk, verifyProofArguments),$$
  where:
    \begin{enumerate}
      \item[] $HNin\kid=H(Nin,\kid^{-1}("register\khk"))$
      \item[] $HNin\kid\khk=H(Nin, \kid^{-1}("register\khk"), \khk^{-1}("register\khk"))$.
    \end{enumerate}
\begin{enumerate}[leftmargin=0cm]
	\item[] \underline{Pseudo-solidity code}

	\hfill\begin{minipage}{\dimexpr\textwidth-20px}
	\begin{lstlisting}[language=Solidity]
	mapping(uint => uint) public ninKidKhUsed;
	mapping(uint => bool) public isPerson;

	function registerKh(
		uint hNinKid,
		uint hNinKidKh,
		uint Kh,
		uint[2] memory proofPointA,
		uint[2][2] memory proofPointsB,
		uint[2] memory proofPointC
	) public {
		//Setting public arguments
		uint[] memory inputValues = new uint[](3);
		inputValues[0] = hNinKid;
		inputValues[1] = hNinKidKh;
		inputValues[2] = Kh;

		require(
			verifyProof(proofPointA, proofPointsB, proofPointC, inputValues)
		);

		ninKidKhUsed[hNinKid] = hNinKidKh;
		isPerson[Kh] = true;
	}
	\end{lstlisting}
	\xdef\tpd{\the\prevdepth}
	\end{minipage}

	\item[] Features
	\begin{itemize}
		  \item[] \textbf{Sybil resistance} \\ $\khk$ is a unique public key bound to the Person on the \pbc{}. By design, the Person cannot have two valid $\khk$ keys at the same time.

@@

	\item[] Remarks
	\begin{itemize}
	\item[i)] Reasoning behind the choice of arguments:
	We want to connect $Nin$ with $\khk$ in a unique, but untraceable way.
	If we only used $HNin\kid\khk$ then if someone used multiple $\khk$s we wouldn't be able to prove the connection to $Nin$ (i.e. they could register a lot of $\khk$s).
	Hashing connects arguments, and makes them opaque without the knowledge of arguments (which in this case include private keys), so the arguments are opaque without the knowledge of private keys.
	\end{itemize}

Statements we need to check:
\begin{itemize}
	\item[1)] $register\kid$ is still valid
	\item[2)] $HNin\kid$ is valid
	\item[3)] $HNin\kid\khk$ is valid
	\item[4)] $\khk$ is valid
	\item[5)] TODO: $\khk$ invalidation!?
\end{itemize}

\begin{lstlisting}[language=circom]
	pragma circom 2.0.0;
\end{lstlisting}

@@
